---
title: "finalProjAboutMarioKart"
author: "Rowan Ess, Anna Prack"
date: "2025-04-22"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---

```{r, warning=FALSE,message=FALSE}
library(tidyverse)
library(openintro)
```

## Data Introduction

This paper will be utilizing the mariokart data set from openintro.\
This data set was collected by recording the auction data from 143 listings for Mario Kart for the Nintendo Wii.\
This data was collected in October 2009.\
This data set has 12 variables, however we will be focusing on three, the final sale price, the shipping price, and the number of wheels included.\

```{r}
mariokart
```

### Variables

total_pr: total price (numerical)\
ship_pr: shipping price (numerical)\
wheels: numbers of wheels included (numerical)\

## Research Questions:

Question: How does the quantity of wheels affect the auction price for a Mario Kart Wii game?\
Null: The quantity of wheels does not affect the auction price.\
Alternative: The quantity of wheels affects the auction price.\

### Errors

Type 1: We conclude that the price changes based on the wheels, even though it does not.\
Type 2: We conclude that the price does not change based on the wheels, even though it did.\
Type 1 would be worse, because the conclusion it draws could be construed as actionable information, leading to a greater consequence.\

### Supporting Questions

How independent is the number of wheels as a variable?\
How to other variables effect the auction price?\
How does the number of wheel effect the shipping price?\

### Expectations

We expect that increasing the number of wheels will increase the auction price.\

## Main Analyses:

The primary purpose of this assessment is to find what effect the quantity of steering wheels has on the sale price of Mario Kart Games. This requires finding the actual price of the auctioned goods.\

As the data set does not provide ending auction price as its own variable, we must subtract shipping price from the total price

```{r}
mariokart <- as_tibble(mariokart)
mariokart %>%
  mutate (auction_pr = total_pr - ship_pr)
```
